Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-02 paper/paper.tex
Tweaking
I tried ILF, it's not very helpful and is hard to explain

@@

@@

\begin{algorithm*}[tb]
\DontPrintSemicolon
\begin{multicols}{2}
\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\shortoverline{\mathcal{P}},
        \shortoverline{\mathcal{T}}),$
        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
    \nl \ForEach{$v \in \V(\mathcal{P})$}{
        \nl $D_v \gets \V(\mathcal{T})$\;
        \nl \ForEach{$(P,\,T) \in L$}{
            \nl $D_v \gets D_v \cap \{ w \in D_v : $ \\
            \hspace*{7em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
            \hspace*{7em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
        }
        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
    }
    \nl \lIf{\FuncSty{propagate}(D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
}
\bigskip
\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried}}{
            \nl \KwSty{continue} \;
        }
        \nl $D' \gets \FuncSty{clone}(D)$ \;
        \nl $D'_v \gets \{ v' \} $ \;
        \nl \If{\FuncSty{propagate}(D')}{
            \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{
                \nl $\KwSty{return}~\KwSty{true}$ \;
            }
        }
    }
}
\bigskip
\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \While{\KwSty{true}}{
        \nl \If{\textnormal{no effectively-unit (treating all wildcard values as a single value)
        domains remain}}{
            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
                \nl $\KwSty{return}~\KwSty{false}$ \;
            }
        }
        \nl \If{\textnormal{no effectively-unit domains remain}}{
            \nl $\KwSty{return}~\KwSty{true}$ \;
        }
        \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard value if there is more
        than one \;
        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
            \nl \ForEach{$(P,\,T) \in L$}{
                \nl \If{$v \sim_P w$}{
                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
                }
            }
            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
        }
    }
}
\bigskip
\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
\nl $(F,\,H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
    \nl $F \gets F + v$ \;
    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
    \nl \lIf{$D_v = \emptyset~\KwSty{or}~\left|A\right| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
    \nl \lIf{$\left|A\right| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
}
\nl $\KwSty{return}~\KwSty{true}$ \;
}
\end{multicols}
\vspace*{0.4cm}% bug in algorithm2e + multicol: incorrect space left above the vertical line
\caption{An algorithm for the $k$-less subgraph isomorphism problem.}
\label{algorithm:sip}
\end{algorithm*}

>>>>

?? Explain effectively-unit domain, multiple $\bot$ values.

@@

?? Talk about iterating, what to do when a vertex disappears from all target graphs.

@@

\begin{algorithm*}[tb]
\DontPrintSemicolon
\begin{multicols}{2}
\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\shortoverline{\mathcal{P}},
        \shortoverline{\mathcal{T}}),$
        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
    \nl \ForEach{$v \in \V(\mathcal{P})$}{
        \nl $D_v \gets \V(\mathcal{T})$\;
        \nl \ForEach{$(P,\,T) \in L$}{
            \nl $D_v \gets D_v \cap \{ w \in D_v : $ \\
            \hspace*{7em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
            \hspace*{7em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
        }
        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
    }
    \nl \lIf{\FuncSty{propagate}(D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
}
\bigskip
\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried}}{
            \nl \KwSty{continue} \;
        }
        \nl $D' \gets \FuncSty{clone}(D)$ \;
        \nl $D'_v \gets \{ v' \} $ \;
        \nl \If{\FuncSty{propagate}(D')}{
            \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{
                \nl $\KwSty{return}~\KwSty{true}$ \;
            }
        }
    }
}
\bigskip
\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \While{\KwSty{true}}{
        \nl \If{\textnormal{no effectively-unit domains (treating all wildcard values as a single
        value) remain}}{
            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
                \nl $\KwSty{return}~\KwSty{false}$ \;
            }
        }
        \nl \If{\textnormal{no effectively-unit domains remain}}{
            \nl $\KwSty{return}~\KwSty{true}$ \;
        }
        \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard value if there is more
        than one \;
        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
            \nl \ForEach{$(P,\,T) \in L$}{
                \nl \If{$v \sim_P w$}{
                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
                }
            }
            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
        }
    }
}
\bigskip
\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
\nl $(F,\,H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
    \nl $F \gets F \cup \{ v \}$ \;
    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
    \nl \lIf{$D_v = \emptyset~\KwSty{or}~\left|A\right| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
    \nl \lIf{$\left|A\right| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
}
\nl $\KwSty{return}~\KwSty{true}$ \;
}
\end{multicols}
\vspace*{0.4cm}% bug in algorithm2e + multicol: incorrect space left above the vertical line
\caption{An algorithm for the $k$-less subgraph isomorphism problem.}
\label{algorithm:sip}
\end{algorithm*}
